---
output: 
md_document:
  html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# envair 

## Overview

This is an R packages developed by the BC Ministry of Environment and Climate Change Strategy  Knowledge Management Branch/Environmental and Climate Monitoring Section (ENV/KMB/ECMS) air quality monitoring unit. The package allows retrieval and processing of air quality monitoring data.

## Installation 

You can install `envair` directly from this GitHub repository. To proceed, you will need the [remotes](https://cran.r-project.org/package=remotes) package:

```{r, eval=FALSE}
install.packages("remotes")
```

Next, install and load the `envair` package using `remotes::install_github()`:

```{r, eval=FALSE}
remotes::install_github("bcgov/envair")
library(envair)
```

## Functions

`GET_STATION_DETAILS_FTP()`  Retrieves station details

`GET_VALID_DATA_PARAMETER()` Retrieves data that has completed ENV's annual validation process. Parameters include PM25, PM10, NO, NO2, SO2, TRS, H2S

`GET_RECENT_DATA_STATION_FTP()` Retrieve the most recent data. 



